### 2024-09-17 README.Rmd
investigate sample size for adding change_N functionality. Initiate test run script for adding functionality.

The structure and functionality of this package resembles surveyISS with some notable differences that accomodate the neuances of fishery-dependent data. These are covered in the next section, "Important Notes".

@@

### Input Data
The following conditions of an input data frame for any species must be met:
1. (length data) There exists a WEIGHT1 column that represents the haul-level proportions-at-length of the observed lengths. This is calculated by dividing the frequency of the observed length within a haul by the total number of fish lengthed in that haul. It should be a standard calculation that is exactly the same for every species. This convention...

@@

@@

@@

>>>>

The structure and functionality of this package resembles surveyISS with some notable differences that accommodate the nuances of fishery-dependent data. These are covered in the next section, "Important Notes".

@@

### Input Data
The following conditions of an input data frame for any species must be met:
1. (length data) There exists a WEIGHT1 column that represents the haul-level proportions-at-length of the observed lengths. This is calculated by dividing the frequency of the observed length within a haul by the total number of fish lengthed in that haul. It should be a standard calculation that is exactly the same for every species.

@@

5. For EBS Pcod, age data has only been used when there exists alredy pre-processed length data associated with it. I.e., I matched the y2 length data object recieved from Steve with age data I downloaded when testing the baseISS functionality on age data. This was necessary becasue I needed quantities like YAGM_SNUM to perform the weighted expansion.

@@

2. You can't chose the species from a big data set containing all the species. This is because data sets for each species should include unique columns necessary to apply their unique expansion methods. For EBS Pcod for example, these columns are only available after much pre-processing and calculating of the raw data.

@@

- subsampling
